---
title: "p8105_hw6_gl2458"
author: "Rachel Lee"
data: "01/08/2020"
output: gihub_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(mgcv)
library(purrr)
library(mlbench)
library(ggplot2)
library(broom)
library(patchwork)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

Problem 1: 
a) Import and clean childbirth dataset.Convert numeric to factor and check for missing data. 

```{r p1_data_import_tidying, message=FALSE}
child_data = read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex))%>% 
  mutate(frace = as.factor(frace))%>% 
  mutate(mrace = as.factor(mrace))%>% 
  mutate(malform = as.factor(malform)) %>% 
  mutate(parity = as.factor(parity)) %>% 
  select(-pnumlbw, -pnumsga) %>%  
  select(bwt, babysex, everything())
```

By mutating, babysex, father's race, mother's race, presence of malformations, and parity are converted to factors from numeric. Previous number of low birth weight babies (pnumlbw) and number of prior small for gestational age babies (pnumsga) are excluded from the data.


b) Propose a regression model


